---
title: "Lines Between Polygons"
author: "Mark Gallivan"
date: ""
output: 
  md_document:
    variant: markdown_github
---
## Set up
Purpose: To calculate the number of lines that intersect two polygons. 

First, let's create a toy example. 
```{r setup}
rm(list = ls())
library(data.table)
library(raster)
library(sp)
library(sf)
library(ggplot2)

## Create lines object
cds1 <- rbind(c(-50, 50), c(50,50))
cds2 <- rbind(c(-50, -50), c(50,-50))
cds3 <- rbind(c(-50, 70), c(50,-70))
cds4 <- rbind(c(10, 10), c(20,60))
cds5 <- rbind(c(-70, 70), c(70,70))

lines <- sf::st_as_sf(spLines(cds1, cds2,cds3, cds4, cds5, attr=data.frame(Lid=1:5)))

## Create polygon object
p1 <- rbind(c(0,0), c(0,90), c(-90, 90), c(-90,0))
p2 <- rbind(c(0,0), c(0,90), c(90, 90), c(90,0))
p3 <- rbind(c(0,0), c(0,-90), c(-90, -90), c(-90,0))
p4 <- rbind(c(0,0), c(90,0), c(90, -90), c(0,-90))

pols <- sf::st_as_sf(spPolygons(p1, p2,p3, p4,attr=data.frame(Pid=1:4)))

## Plot polygons and lines
ggplot(pols) + geom_sf() + geom_sf(data = lines, color = "blue")
```

## Solution 
Here's a function to that requires an Pid column in the polygon object and a Lid column in the linestring object.

```{r Solution}
## Function taking in polygon and linestring sf objects. Need a Pid column in the polygon object and Lid column in the linestring object. 

GetNumberOfIntersectingLines <- function(PolygonObj = pols, LineObj = lines) {
  # find intersections
  dt <- suppressWarnings(as.data.table(sf::st_intersection(lines, pols)))

  CJFunc <- function(ID =1) {
    TmpDat <- CJ(as.numeric(t(dt[Lid == ID, .(Pid)])), as.numeric(t(dt[Lid == ID, .(Pid)])))
    TmpDat <- TmpDat[V1 != V2]
  }

  testDat <- rbindlist(lapply(dt[, unique(Lid)], CJFunc))

  setnames(testDat, old = c("V1","V2"), new = c("Pid_1", "Pid_2"))

  testDat <- testDat[, .N, by = .(Pid_1,Pid_2)]

  return(testDat)
}

testDat <- GetNumberOfIntersectingLines(PolygonObj = pols, LineObj = lines)
testDat
```

This function outputs an edge list with the number of intersecting lines between each polygon with at least one line intersecting both polygons. The polygons IDs are positioned such that the top left represents Pid = 1, top right represents 2, bottom left represents 3, bottom right represents 4. So there are three lines crossing between the top left polygon and the top right polygon. Note that the long diagonal line is considered to intersect all four polygons since they share the 0,0 coordinate.